%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt]{moderncv}

\usepackage[sfdefault]{cabin}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage{amssymb}

\usepackage[scale=0.8]{geometry}


% https://tex.stackexchange.com/questions/158803/add-a-table-of-contents-into-a-moderncv-document
\makeatletter
\newcommand\@pnumwidth{1.55em}
\newcommand\@tocrmarg{2.55em}
\newcommand\@dotsep{4.5}
\makeatother
\usepackage{titletoc}

\makeatletter
\setlength\columnsep{20pt}
\setcounter{tocdepth}{1}
\newcommand\contentsname{Contents}
\newcommand\tableofcontents{%
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
\section*{\contentsname}
\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
    \@starttoc{toc}%
    }
\usepackage{titletoc}
\titlecontents*{section}[0pt]
  {}{}{}
  {, \itshape\thecontentspage}[\ \textbullet\ ][.]
\renewcommand\l@subsection[2]{}
\makeatother


\usepackage{xstring}
\usepackage{soul}
\setul{2pt}{1pt}
\def\FormatName#1{%
  \IfSubStr{#1}{Poon}{\ul{\textbf{#1}}}{#1}%
}


\makeatletter\renewcommand*{\bibliographyitemlabel}{\arabic{enumiv}.}\makeatother

\usepackage[resetlabels]{multibib}
\newcites{book,misc}{{Books},{Others}}





\name{Art F.~Y.}{Poon}
%\title{Curriculum vitae}
\address{Health Sciences Addition, H422}{London, ON}{Canada N6A 5C1}
\phone[office]{(519) 661-2111 ext.~87978}
\email{apoon42@uwo.ca}
\social[github]{ArtPoon}
\social[twitter]{art\_poon}

\begin{document}

\makecvtitle
\tableofcontents


\section{Education}

\cventry{2000--2005}{PhD}{University of California, San Diego}{La Jolla}{Biology}{Thesis: Evolutionary consequences of the genetic environment on mutations in bacterial viruses (Dr.~Lin Chao)}
\cventry{1998--2000}{MSc}{University of British Columbia}{Vancouver}{Zoology}{Thesis:  The evolution of the genetic load caused by recurrent mutations in small populations: genetic context and demographic history (Dr.~Sarah P.~Otto)}
\cventry{1994--1998}{HonBSc}{University of Toronto}{Toronto}{Biology}{Thesis: Estimates of mutational variance in \textit{Drosophila melanogaster} (Dr.~David Houle)}


\section{Appointments}

\cventry{August 2016--present}{Assistant Professor}{Department of Pathology and Laboratory Medicine}{Western University}{}{Primary appointment.}

\cventry{June 2017--present}{Assistant Professor}{Department of Microbiology and Immunology}{Western University}{}{Cross-appointment.}

\cventry{November 2016--present}{Assistant Professor}{Department of Applied Mathematics}{Western University}{}{Cross-appointment.}

\cventry{March 2012--July 2016}{Assistant Professor, non-tenure track}{Department of Medicine}{University of British Columbia}{}{As an employee of Providence Health Care, I was held this honorary unpaid appointment to provide teaching, scholarly and service activities at the university.}

\cventry{October 2015--July 2016}{Senior Research Scientist}{}{BC Centre for Excellence in HIV/AIDS}{}{}

\cventry{October 2009 -- October 2015}{Associate Research Scientist, Bioinformatics}{}{BC Centre for Excellence in HIV/AIDS}{}{}

\cventry{July 2010 -- June 2015}{Adjunct Assistant Professor}{Faculty of Health Sciences}{Simon Fraser University}{}{}

\cventry{August 2008 -- August 2010}{Postdoctoral Fellow}{Department of Experimental Medicine}{University of British Columbia}{}{Supervisor: Dr.~P.~Richard Harrigan.}

\cventry{August 2005 -- July 2008}{Postdoctoral Fellow}{Antiviral Research Center}{University of California, San Diego}{}{Supervisor: Dr.~Simon Frost.}



\section{Awards and Recognitions}

\cventry{2013--2018}{CIHR New Investigator Award}{CIHR Priority Announcement: CHVI Vaccine Discovery and Social Research}{CAD\$300,000}{}{Project title: Applied phylogenetics for HIV prevention.}

\cventry{2012-2020}{Career Investigator Scholar Award}{Michael Smith Foundation for Health Research, St.~Paul's Hospital Foundation, and the Providence Health Care Research Institute}{CAD\$ 317,500}{}{Project title: Phylogenetic surveillance of the HIV epidemic in British Columbia.  In 2016, I declined the remainder of this award when I left British Columbia to accept a tenure-track appointment at Western University in Ontario.}

\cventry{2008-2010}{CIHR Fellowship}{CIHR Fellowships Award in the Area of Biomedical/Clinical HIV/AIDS Research}{CAD\$97,500}{}{}

\cventry{1998-2000}{Postgraduate Scholarship Award}{Natural Sciences and Engineering Research Council of Canada (NSERC)}{CAD\$37,000}{}{}


\section{Publications}


\renewcommand{\refname}{Peer-reviewed articles}
%\renewcommand{\bibliographyitemlabel}{{\arabic{enumiv}.}}

71 peer-reviewed articles; 33 as first or senior author.

\nocite{*}

\bibliographystyle{custom}
\bibliography{publications}

\vspace{1em}
\nocitebook{*}
\bibliographystylebook{custom}
\bibliographybook{books}


\end{document}




