\documentclass[12pt,a4paper]{article}

\usepackage[margin=2cm]{geometry}
\usepackage{times}
\usepackage{fancyhdr}
\pagestyle{fancy}

\lhead{CV (2-page)}
\chead{Art F.~Y.~Poon}
\rhead{Last compiled: \today}

% section labels
\usepackage[small,compact,explicit]{titlesec}
\titleformat{\section} {\vspace{4pt}\bf}{\thesection} {12pt} {#1\vspace{-4pt}}
\titleformat{\subsection} {\vspace{2pt}\bf}{\thesubsection} {12pt} {\uline{#1}\vspace{-4pt}}
\titleformat{\subsubsection}[runin]{\vspace{0pt}\bf}{\thesubsubsection} {6pt} {#1}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, nosep}
\setlist[enumerate]{leftmargin=*, nosep}


\usepackage[numbers]{natbib}
\setlength{\bibsep}{0pt plus 0.3ex}



\begin{document}

% Please append up to 5 short CVs (2 pages each) of the lead investigator(s) and collaborators.  (There will typically be more than 5 members on a team.)  A short CV should include degrees,  current position(s),  selected peer-reviewed publications (last 6 years), other evidence of impact and contributions (last 6 years), and numbers of undergraduate, master’s level, PhD level and postdoctoral trainees (last 6 years). 
\section * {Degrees}
\begin{itemize}
\item 2000--2005: PhD (Experimental evolution), University of California, San Diego. 
\item 1998--2000: MSc (Mathematical biology), University of British Columbia.
\item 1994-1998: HonBSc (Biology), University of Toronto
\end{itemize}


\section * {Current appointment}
\begin{itemize}
\item July 2019--present: Associate Professor (tenured), Department of Pathology \& Laboratory Medicine, Western University. 
%(Cross-appointments with the Department of Applied Mathematics and the Department of Microbiology \& Immunology.)
\end{itemize}


\renewcommand{\refname}{Selected peer-reviewed publications\\{\normalfont{Selected from 43 publications in the last 6 years (2014-2019).}}}

\nocite{*}

\bibliographystyle{naturemag}
\bibliography{selected}


\vspace{0pt}
\section * {Other evidence of impact and contributions (last 6 years)}

\begin{itemize}
\itemsep 3pt

%\item 2016/7: Invited Member of Special Emphasis Panel/Scientific Review Group (Phylodynamics). National Institutes of Health.

\item A study of hepatitis C virus phylodynamics under my direction and co-authored with my trainees (Joy et al.~2016; Lancet Inf Dis) is directly referenced in the U.S.~National Viral Hepatitis Action Plan (2017-2020), and was featured by several media outlets including the Globe and Mail, CBC News, Global News, and the Toronto Star.

\item I was the sole developer of an automated phylodynamic monitoring system of an HIV population treatment database in British Columbia, which led to the world's first example of such a system being used to support a public health response to an outbreak of transmitted HIV drug resistance in near real time (Poon \textit{et al.}~2016, Lancet HIV).  This paper was featured by the Joint United Nations Programme on HIV/AIDS (UNAIDS).

\item 2013--2018: \textbf{New Investigator Award.} Canadian Institutes for Health Research (CIHR Priority Announcement: CHVI Vaccine Discovery and Social Research).  CAD\$300,000.

\item 2012-2020 (declined in 2017):  \textbf{Career Investigator Scholar Award.}  Michael Smith Foundation for Health Research, St.~Paul's Hospital Foundation, and the Providence Health Care Research Institute. CAD\$ 317,500.


\end{itemize}


\section * {Trainee supervision}

Total numbers of trainees in the last 6 years: 6 PDFs, 2 PhD, 5 MSc, 2 MSc-equivalent.\\[-6pt]

\begin{itemize}

\item[] \textbf{Western University:}

\item{2019/8 -- present:}  {Roux-Cil Ferreira.} {Postdoctoral associate.}

\item{2019/8 -- present:} {David Champredon.} {Postdoctoral associate.}

\item{2019/9 -- present:} {Wan-Yu (Elisa) Chao.} {MSc student.}

\item{2018/9 -- present:} {John Palmer.} {MSc student.}
\item{2018/8 -- present:} {Connor Chato.} {MSc student.}

\item{2017/9 -- present:} {Abayomi Olabode.} {Postdoctoral associate.} 

\item{2016/10 -- 2019/8:} {Mariano Avino.} {Postdoctoral associate.} 

\item{2016/11 -- 2018/5:} {Erika Chadwick.} {MCISc Pathologists' Assistant Graduate Program.}

%\item{2017/10 -- 2018/4:} {Reid Vender.} {Undergraduate thesis supervisor.}

%\item{2017/10 -- 2018/4:} {John Palmer.} {Undergraduate thesis supervisor.}

%\item{2016/10 -- 2017/4:} {Cornelius Nesen.} {Undergraduate thesis supervisor.}

%\item{2016/10 -- 2017/4:} {Enid Chan.} {Undergraduate thesis supervisor.}


%\item[] \textbf{Department of Microbiology \& Immunology, Western University.}
\item{2018/8 -- present:} {Laura Mu\~noz Baena.}{PhD student.}

%\item[] \textbf{Department of Applied Mathematics, Western University.}
\item{2016/11 -- present:} {David Dick.} {PhD student, co-supervisor.} 


\item[] \textbf{Department of Bioinformatics, University of British Columbia:}


\item{2013/9 -- 2016/6:} {Thuy Nguyen.} {MSc student.}

\item{2014/9 -- 2016/7:} {Rosemary McCloskey.} {MSc student.}


\item[] \textbf{BC Centre for Excellence in HIV/AIDS:}
\item{2016/5 -- 2016/8:} {David McVea.} {Masters of Public Health, research supervisor.}



%\item{2016/1 -- 2016/8:} {Bradley Jones.} {Undergraduate research co-op.}

%\item{2015/1 -- 2015/8:} {Joshua Horacsek.} {Undergraduate research co-op.}

\item{2013/1 -- 2016/1:} {Jeffrey B.~Joy.} {Postdoctoral fellow.}

\item{2011/7 -- 2015/8:} {Richard H.~Liang.} {Postdoctoral fellow.}

\end{itemize}



\end{document}
